\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-09-20 gwnnDraft02.tex
some fixes

\label{sec:gw}
%Sectors other than the SM can be reheated through multifield inflationary theories, Reheaton models, etc. In these models, the SM will receive the majority of the energy density while the remaining energy density will be distributed, in a model dependent way, to the various hidden sectors. If there does not exist a portal between the sectors, they will remain decoupled and evolve independently. When looking at multiple thermally decoupled hidden sectors it is convenient to define the temperature ratio [cite cold,dark,noisy]
%\begin{equation}
%\xi_i \equiv  \frac{T_{i}}{T_{\gamma}}
%\end{equation}
%Where $T_{i}$ is the temperature of the $i^{th}$ hidden sector, and $T_{\gamma}$ the temperature of the standard model (assuming radiation domination).

@@

A SFOPT proceeds through bubble nucleation, where bubbles of the hadronic phase form in the vacuum of the quark phase. These bubbles will expand, eventually colliding and merging until the entire sector is within the new phase.  These bubbles are described by the following Euclidean action~\cite{Linde:1981zj}
%
\begin{equation}\label{eqn:EuclideanAction}
S_{E}(T) = \frac{1}{T}\int d^3x \bigg[\frac{1}{2}(\nabla\phi)^2 + V(\phi,T)  \bigg],
\end{equation}
where the time component has been integrated out due to nucleation occuring, not in vaccum, but in a finite temperature plasma. $\phi$ is the symmetry breaking scalar field with a non-zero VEV. In the case of the chiral phase transition, the scalar field breaking the SU$(N_f)_{R}$ $ \times$ SU$(N_f)_{L}$ chiral symmetry is the effective quark condensate $\phi_{i} \sim \langle q\bar{q} \rangle_{i}$ of the respective sector. We leave the thermalized potential $V(\phi, T)$ general. As previously stated, an exact QCD potential at the time of the chiral phase transition is not well understood outside of lattice results. In~\cite{Bai:2018dxf} chiral effective Lagrangian was used to calculate a low energy thermalized potential for confining SU$(N)$.

The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves. Assuming that the SM sector is radiation dominated, a quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition $\epsilon$ to the energy density of radiation, at the time of nucleation~\citep{Espinosa:2010hh} ,
\begin{equation}
\alpha     \equiv  \frac{\epsilon}{g_{*} \pi^2 (T^{nuc}_{\gamma})^4/30},
\label{eq:alpha}
\end{equation}
with $\epsilon$ being calculable from the scalar potential. Assuming that there is a negligible amount of energy being dumped back into the SM, which would cause significant reheating of $\rho_{\gamma}$,  the latent head, $\epsilon$ should correspond to the energy density of the hidden sector going through the PT. The parameter $g_{*}$ in the denominator of Eq.~(\ref{eq:alpha}) is the number of relativistic degrees of freedom at the time of the phase transition, with contributions from species in both the visible and dark sectors. It has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities).
\begin{equation}\label{eqn:RelaDOF}
g_{*} = g_{*,\gamma} + \sum_{i} g_{*,i} (\xi_{i})^4
\end{equation}
with $\xi$ being the temperature ratio defined in Eq.~(\ref{eq:xi}). The bounds from effective number of neutrinos ~\citep{} mean that $\xi_i \lesssim 1$ for all $i$, so $g_{*} \approx g_{*,\gamma}$. In the case of dark QCD-like chiral  phase transitions, the temperature of the phase transition is on the the order of the symmetry breaking scale of the respective sector, $T_{h}^{i} \sim \mathcal{O}(\Lambda_{QCD,i})$. The work of~\citep{Bai:2018dxf} calculated $\alpha$ with an effective chiral Lagrangian have found various upper bounds. We take the optimistic scenario where the numerator is bounded above by the symmetry breaking scale, 
%
\begin{equation}
\alpha_i \approx \xi_i^{4} \approx \bigg( \frac{\Lambda_{QCD,i}}{T_{\gamma}^{nuc}}\bigg)^4
\end{equation}
%
where $T_{\gamma}^{nuc}$ is the temperature of the SM photon bath at the time of the phase transition. Another important parameter to characterize the phase transition is its inverse timescale, $\beta$~\citep{Caprini:2015zlo}. The inverse timescale can be calculated using the action in Eq.~(\ref{eqn:EuclideanAction}),

\begin{equation}
\beta  \equiv \frac{dS_{E}(T)}{dt}\bigg|_{t = t_{nuc}}
\end{equation}

@@

\begin{equation}
\frac{\beta}{H} = T^{nuc}_h \frac{dS_{E}(T)}{dT}\bigg|_{T = T^{nuc}}.
\end{equation}

Due to the lack of an analytic potential, we take $\beta/H$ to be a standard value currently seen in the field~\cite{}. There has been a lot of work in recent years in the estimation of $\beta/H$ using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models~\citep{Helmboldt:2019pan}. \draftnote{Are there other papers? One paper is not a lot of work}. Although, these studies claim a large range of values and thus a consensus has \draftnote{not?} yet been reached.
\subsection{Production of Gravitational Waves}
\label{sec:signals}

Gravitational waves are produced with contributions from different components of the SFOPT's evolution.  It is commonplace to parameterize the spectral energy density in gravitational waves by~\citep{PhysRevD.75.043507} 
\begin{equation}
\Omega_{\textrm{GW}} (f) \equiv \frac{1}{ \rho_{c}} \frac{d \rho_{\textrm{GW}}(f) }{d \textrm{\,log}(f)} , 
\end{equation}
where $\rho_{c} = 3H^2/(8 \pi G)$ is the critical energy density. The three leading order contributions to the GW power spectrum are as follows:
\begin{itemize}
\item \textbf{Scalar field contributions $\Omega_{\phi}$}: Caused by collisions of the bubble walls, the solutions being completely dependent on the scalar field configuration. With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$~\citep{PhysRevD.45.4514, Huber_2008}. 
\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ enhanced gravitational waves. With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$~\citep{PhysRevLett.112.041301}.
\item \textbf{Magnetohydrodynamical contributions $\Omega_{B}$}: MTG shocks within the plasma, left over from the sound wave propagation, will produce gravitational waves. With efficiency factor $\kappa_{
turb} \approx 0.1 \kappa_{v} $~\citep{PhysRevD.74.063521}.
\end{itemize}

Where $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$. Explicitly \cite{Breitbach:2018ddu, Caprini:2015zlo, Espinosa:2010hh}, 
\begin{equation}\label{eqn:critPTstrength}
\alpha_{\infty} = \frac{(T^{nuc}_h)^2}{\rho_R}\left[\sum_{bosons} n_i\frac{\Delta m^2_i}{24} + \sum_{fermions} n_i\frac{\Delta m_i^2}{48}\right],
\end{equation} 
for particles with $n_i$ degrees of freedom that obtain mass through the phase transition. 
Exotic sectors feature no baryons \draftnote{why??} and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness \draftnote{isn't that what we're talking about?}\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.

The total gravitational wave signal is a linear combination of the three contributions,
\begin{equation}
h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi} + h^2\Omega_{v} + h^2\Omega_{turb} 
\end{equation}
In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$.

Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime. Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$). In this case, the efficiency factors for sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.  The form of the GW power spectrum at the time of nucleation is given by~\citep{Breitbach:2018ddu},

\begin{equation}
h^2\Omega_{\textrm{GW}}^* = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
\end{equation}
\draftnote{Why is there a * on the $\Omega$?} Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles. $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions.
\begin{equation}\label{eqn::spectralshape}
S(f) = \frac{3.8 \,(f/f_p)^{2.8}}{1 + 2.8\,(f/f_p)^{3.8}}
\end{equation}
The peak frequency, $f_{p}$ is a function of the temperature of the SM at the time of nucleation.  The various hidden sectors can phase transition at different scales and therefore temperatures, causing a shift in the GW spectrum's peak frequency given by~\cite{Huber_2008},
%
\begin{equation}
f_{p} = 3.8 \times 10^{-8} \, \textrm{Hz}\, \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}},
\end{equation}
%
where $g_*$  is calculated using Eq.~(\ref{eqn:RelaDOF}) , although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant.

@@

\begin{equation}\label{eqn::redshifting}
\mathcal{A} \equiv \bigg( \frac{a}{a_{0}} \bigg)^4 \bigg( \frac{H}{H_{0}}\bigg)^2
\end{equation}
where $a$ ($a_{0}$)  and $H$ ($H_{0}$) are the scale factor and Hubble constant at the time of nucleation (observation), respectfully. Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW signal that would be measured today is given by the coherent sum,
\begin{equation}
\Omega_{\textrm{GW}}^{0} =  \sum_{i}^{N} \mathcal{A}^{i}\, \Omega_{\textrm{GW}}^{i,*}((a_{0}/a)_{i} f) 
\end{equation}
It is safe to assume that a subset of parameters of the SFOPT do not differ between sectors within $N$natrualness or other decoupled hidden sector models.\draftnote{what?} In the case of N-copies of dark QCD-like phase transitions, the relativistic degrees of freedom, phase transition rate,  the dark QCD scale, are all similar. This makes the redshifting factor, $\mathcal{A}^i$, independent of sector number.

\begin{figure}[h!]
\centering
\includegraphics[scale=.3]{Nnatral.png} 
\caption{ Gravitational wave power spectrum for standard $N$naturalness using the scalar reheaton model of section~\ref{sec:reheat}. All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green). \draftnote{The sum curve and the i=5 curve aren't visible.}  }
\label{fig::Nnatural}
\end{figure}
Applying this to the standard reheating scenario of $N$natrualness, introduced in~\ref{sec:reheat}, we get GW signals as seen in figure~(\ref{fig::Nnatural}). Plotted are the individual contributions to the signal from each phase transitioned sector, as well as the coherent sum of all sectors. Future GW interferometers and pulsar timing array sensitivity curves are shown in comparison to the signal. The sensitivity curves are interpreted as the region of possible detection if intersected with the GW signal, more detail in the construction of these curves is given in Section~\ref{sec:detection}. Notice that the total signal is dominated by the first sectors contribution. This is caused by the quartic temperature ratio suppression in Eq.~(\ref{eq:alpha}) and the large temperature gaps between adjacent sectors. Such a suppression leads to standard $N$natrualness evading future detector thresholds by a few orders of magnitude in units of energy density. This is not the case if we consider the more generalized reheating scenarios of section~\ref{sec:constraints}.

@@

\begin{figure*}[tb]
\centering
\begin{minipage}[c]{\textwidth}
\includegraphics[width=.45\textwidth]{TwoFar.png} 
\hfill
\includegraphics[width=.45\textwidth]{TwoMed.png} 
\hfill
\includegraphics[width=.45\textwidth ]{highest.png}
\hfill
\includegraphics[width=.45\textwidth]{energydensity.png} 
\end{minipage}
\hfill
\caption{ Gravitational wave power spectrum for various models. The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures. The bottom left (right) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$ ). All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
\label{fig:Haa}
\end{figure*}

\subsection{Detection of Stochastic Graviational Waves}
\label{sec:detection}

A unpolarized stocastic gravitational wave background could be detectable if the the signal-to-noise ratio (SNR) is above some threshold value, $\rho > \rho_{th}$, dictated by the capabilities of future interferometers and pulsar timing arrarys (PTA). These interferometers/PTAs quote their experimental sensistivies in terms of spectral noise curves, $S_{\textrm{eff}}(f)$, which can be translated into units of energy density through $h^2 \Omega_{\textrm{eff}}(f) = \frac{2\pi^2}{3H^2}f^3 S_{\textrm{eff}}(f)$. If the experiment uses a single (multiple) detector, the auto-correlated (cross-correlated) SNR is used in comparing to the threshold value $\rho_{th}$. The auto-correlated and cross-correlated SNR are explictely given as~\cite{PhysRevD.59.102001},
\begin{equation}\label{eqn::SNR}
\begin{split}
\rho^2 =  T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)}
\\
\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)}
\end{split}
\end{equation}
Where $T$ is the exposure time of the experiment. The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$. LISA~\citep{Audley:2017drz} and B-DEICIGO~\citep{10.1093/ptep/pty078} are proposed to be single detector interferometers, where as BBO~\citep{PhysRevD.72.083005} and DEICIGO~\citep{Sato_2017} would be built from an array of multiple interferometers.

GW signals produced from an early cosmological phase transition would be seen as a stocastic background. Assuming that the GW follows a power law background in frequency, it is commonplace to quote the power law integrated (PLI) sensistivity curves~\cite{PhysRevD.88.124032}. the PSI curves are constructed using information from the power law form of the signal,
\begin{equation}
h^2 \Omega_{\textrm{GW}}(f) = h^2 \Omega_{\beta}  \bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta}
\end{equation}
where $\beta$ is the spectral index of the power law, and $f_{\textrm{ref}}$ is an arbitrary reference frequency which has no effect on the PLI sensetivities.

The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn:RelaDOF}), for various spectral indices $\beta \in (-8,-7,-6, ... , 6, 7, 8)$ and for some fixed threshold value of $\rho_{th}$. Each curve will lay tangent to the PSI curve, more formally,
\begin{equation}
h^2 \Omega_{\textrm{PLI}} = \max\limits_{\beta}\bigg[ h^2 \Omega_{\beta}\bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta}  \bigg].
\end{equation}

@@

\section{Conclusion}
\label{sec:conclusion}

@@

We can think of these results providing 
This demonstrates the power of GW signals to probe deep into the unknown arena of complex hidden sectors --- whether there are 1, 5, or more hidden sectors

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{apsrev4-1}
\bibliography{refs}

>>>>

\label{sec:gw}
%Sectors other than the SM can be reheated through multifield inflationary theories, Reheaton models, etc. In these models, the SM will receive the majority of the energy density while the remaining energy density will be distributed, in a model dependent way, to the various hidden sectors. If there does not exist a portal between the sectors, they will remain decoupled and evolve independently. When looking at multiple thermally decoupled hidden sectors it is convenient to define the temperature ratio [cite cold,dark,noisy]
%\begin{equation}
%\xi_i \equiv  \frac{T_{i}}{T_{\gamma}}
%Where $T_{i}$ is the temperature of the $i^{th}$ hidden sector, and $T_{\gamma}$ the temperature of the standard model (assuming radiation domination).

@@

A SFOPT proceeds through bubble nucleation, where bubbles of the hadronic phase form in the vacuum of the quark phase. These bubbles will expand, eventually colliding and merging until the entire sector is within the new phase.  These bubbles are described by the following Euclidean action~\cite{Linde:1981zj}
\begin{equation}\label{eqn:EuclideanAction}
S_{E}(T) = \frac{1}{T}\int d^3x \bigg[\frac{1}{2}(\nabla\phi)^2 + V(\phi,T)  \bigg],
where the time component has been integrated out due to nucleation occuring, not in vaccum, but in a finite temperature plasma. $\phi$ is the symmetry breaking scalar field with a non-zero VEV. In the case of the chiral phase transition, the scalar field breaking the SU$(N_f)_{R}$ $ \times$ SU$(N_f)_{L}$ chiral symmetry is the effective quark condensate $\phi_{i} \sim \langle q\bar{q} \rangle_{i}$ of the respective sector. We leave the thermalized potential $V(\phi, T)$ general. As previously stated, an exact QCD potential at the time of the chiral phase transition is not well understood outside of lattice results. In~\cite{Bai:2018dxf} chiral effective Lagrangian was used to calculate a low energy thermalized potential for confining SU$(N)$. 
The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves. Assuming that the SM sector is radiation dominated, a quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition $\epsilon$ to the energy density of radiation, at the time of nucleation~\citep{Espinosa:2010hh} ,
\alpha     \equiv  \frac{\epsilon}{g_{*} \pi^2 (T^{nuc}_{\gamma})^4/30},
\label{eq:alpha}
with $\epsilon$ being calculable from the scalar potential. Assuming that there is a negligible amount of energy being dumped back into the SM, which would cause significant reheating of $\rho_{\gamma}$,  the latent head, $\epsilon$ should correspond to the energy density of the hidden sector going through the PT. The parameter $g_{*}$ in the denominator of Eq.~(\ref{eq:alpha}) is the number of relativistic degrees of freedom at the time of the phase transition, with contributions from species in both the visible and dark sectors. It has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities).
\begin{equation}\label{eqn:RelaDOF}
g_{*} = g_{*,\gamma} + \sum_{i} g_{*,i} (\xi_{i})^4
with $\xi$ being the temperature ratio defined in Eq.~(\ref{eq:xi}). The bounds from effective number of neutrinos ~\citep{} mean that $\xi_i \lesssim 1$ for all $i$, so $g_{*} \approx g_{*,\gamma}$. In the case of dark QCD-like chiral  phase transitions, the temperature of the phase transition is on the the order of the symmetry breaking scale of the respective sector, $T_{h}^{i} \sim \mathcal{O}(\Lambda_{QCD,i})$. The work of~\citep{Bai:2018dxf} calculated $\alpha$ with an effective chiral Lagrangian have found various upper bounds. We take the optimistic scenario where the numerator is bounded above by the symmetry breaking scale, 
\alpha_i \approx \xi_i^{4} \approx \bigg( \frac{\Lambda_{QCD,i}}{T_{\gamma}^{nuc}}\bigg)^4
where $T_{\gamma}^{nuc}$ is the temperature of the SM photon bath at the time of the phase transition. Another important parameter to characterize the phase transition is its inverse timescale, $\beta$~\citep{Caprini:2015zlo}. The inverse timescale can be calculated using the action in Eq.~(\ref{eqn:EuclideanAction}), 
\beta  \equiv \frac{dS_{E}(T)}{dt}\bigg|_{t = t_{nuc}}

@@

\frac{\beta}{H} = T^{nuc}_h \frac{dS_{E}(T)}{dT}\bigg|_{T = T^{nuc}}.
Due to the lack of an analytic potential, we take $\beta/H$ to be a standard value currently seen in the field~\cite{}. There has been a lot of work in recent years in the estimation of $\beta/H$ using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models~\citep{Helmboldt:2019pan}. \draftnote{Are there other papers? One paper is not a lot of work}. Although, these studies claim a large range of values and thus a consensus has \draftnote{not?} yet been reached.
\subsection{Production of Gravitational Waves}
\label{sec:signals}
Gravitational waves are produced with contributions from different components of the SFOPT's evolution.  It is commonplace to parameterize the spectral energy density in gravitational waves by~\citep{PhysRevD.75.043507} 
\Omega_{\textrm{GW}} (f) \equiv \frac{1}{ \rho_{c}} \frac{d \rho_{\textrm{GW}}(f) }{d \textrm{\,log}(f)} , 
where $\rho_{c} = 3H^2/(8 \pi G)$ is the critical energy density. The three leading order contributions to the GW power spectrum are as follows:
\item \textbf{Scalar field contributions $\Omega_{\phi}$}: Caused by collisions of the bubble walls, the solutions being completely dependent on the scalar field configuration. With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$~\citep{PhysRevD.45.4514, Huber_2008}. 
\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ enhanced gravitational waves. With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$~\citep{PhysRevLett.112.041301}.
\item \textbf{Magnetohydrodynamical contributions $\Omega_{B}$}: MTG shocks within the plasma, left over from the sound wave propagation, will produce gravitational waves. With efficiency factor $\kappa_{
turb} \approx 0.1 \kappa_{v} $~\citep{PhysRevD.74.063521}.
Where $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$. Explicitly \cite{Breitbach:2018ddu, Caprini:2015zlo, Espinosa:2010hh}, 
\begin{equation}\label{eqn:critPTstrength}
\alpha_{\infty} = \frac{(T^{nuc}_h)^2}{\rho_R}\left[\sum_{bosons} n_i\frac{\Delta m^2_i}{24} + \sum_{fermions} n_i\frac{\Delta m_i^2}{48}\right],
for particles with $n_i$ degrees of freedom that obtain mass through the phase transition. 
Exotic sectors feature no baryons \draftnote{why??} and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness \draftnote{isn't that what we're talking about?}\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}. 
The total gravitational wave signal is a linear combination of the three contributions,
h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi} + h^2\Omega_{v} + h^2\Omega_{turb} 
In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$. 
Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime. Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$). In this case, the efficiency factors for sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$. Quantities that are calculated at the time of nucleation are denoted with an asterisk (i.e $h^2\Omega_{\textrm{GW}}^*$), which are evolved to relate to their values at the time of observation. The form of the GW energy density at the time of nucleation is given by~\citep{Breitbach:2018ddu},
h^2\Omega_{\textrm{GW}}^* = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles. $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions.
\begin{equation}\label{eqn::spectralshape}
S(f) = \frac{3.8 \,(f/f_p)^{2.8}}{1 + 2.8\,(f/f_p)^{3.8}}
The peak frequency, $f_{p}$ is a function of the temperature of the SM at the time of nucleation.  The various hidden sectors can phase transition at different scales and therefore temperatures, causing a shift in the GW spectrum's peak frequency given by~\cite{Huber_2008},
f_{p} = 3.8 \times 10^{-8} \, \textrm{Hz}\, \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}},
where $g_*$  is calculated using Eq.~(\ref{eqn:RelaDOF}) , although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant. 

@@

\begin{equation}\label{eqn::redshifting}
\mathcal{A} \equiv \bigg( \frac{a}{a_{0}} \bigg)^4 \bigg( \frac{H}{H_{0}}\bigg)^2
where $a$ ($a_{0}$)  and $H$ ($H_{0}$) are the scale factor and Hubble constant at the time of nucleation (observation), respectfully. Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW signal that would be measured today is given by the coherent sum,
\Omega_{\textrm{GW}} =  \sum_{i}^{N} \mathcal{A}^{i}\, \Omega_{\textrm{GW}}^{i,*}((a_{0}/a)_{i} f) 
It is safe to assume that a subset of parameters of the SFOPT do not differ between sectors within $N$natrualness or other decoupled hidden sector models.\draftnote{what?} In the case of N-copies of dark QCD-like phase transitions, the relativistic degrees of freedom, phase transition rate,  the dark QCD scale, are all similar. This makes the redshifting factor, $\mathcal{A}^i$, independent of sector number.
\begin{figure}[h!]
\centering
\includegraphics[scale=.3]{Nnatral.png} 
\caption{ Gravitational wave power spectrum for standard $N$naturalness using the scalar reheaton model of section~\ref{sec:reheat}. All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green).}
\label{fig::Nnatural}
\end{figure}
Applying this to the standard reheating scenario of $N$natrualness, introduced in~\ref{sec:reheat}, we get GW signals as seen in figure~(\ref{fig::Nnatural}). Plotted are the individual contributions to the signal from each phase transitioned sector, as well as the coherent sum of all sectors. Future GW interferometers and pulsar timing array sensitivity curves are shown in comparison to the signal. The sensitivity curves are interpreted as the region of possible detection if intersected with the GW signal, more detail in the construction of these curves is given in Section~\ref{sec:detection}. Notice that the total signal is dominated by the first sectors contribution. This is caused by the quartic temperature ratio suppression in Eq.~(\ref{eq:alpha}) and the large temperature gaps between adjacent sectors. Such a suppression leads to standard $N$natrualness evading future detector thresholds by a few orders of magnitude in units of energy density. This is not the case if we consider the more generalized reheating scenarios of section~\ref{sec:constraints}. 

@@

\begin{figure*}[tb]
\centering
\begin{minipage}[c]{\textwidth}
\includegraphics[width=.45\textwidth]{TwoFar.png} 
\hfill
\includegraphics[width=.45\textwidth]{TwoMed.png} 
\hfill
\includegraphics[width=.45\textwidth ]{highest.png}
\hfill
\includegraphics[width=.45\textwidth]{energydensity.png} 
\end{minipage}
\hfill
\caption{ Gravitational wave power spectrum for various models. The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures. The bottom left (right) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$ ). All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
\label{fig:Haa}
\end{figure*}
\subsection{Detection of Stochastic Graviational Waves}
\label{sec:detection}
A unpolarized stocastic gravitational wave background could be detectable if the the signal-to-noise ratio (SNR) is above some threshold value, $\rho > \rho_{th}$, dictated by the capabilities of future interferometers and pulsar timing arrarys (PTA). These interferometers/PTAs quote their experimental sensistivies in terms of spectral noise curves, $S_{\textrm{eff}}(f)$, which can be translated into units of energy density through $h^2 \Omega_{\textrm{eff}}(f) = \frac{2\pi^2}{3H^2}f^3 S_{\textrm{eff}}(f)$. If the experiment uses a single (multiple) detector, the auto-correlated (cross-correlated) SNR is used in comparing to the threshold value $\rho_{th}$. The auto-correlated and cross-correlated SNR are explictely given as~\cite{PhysRevD.59.102001},
\begin{equation}\label{eqn::SNR}
\rho^2 =  T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)}
\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)}
Where $T$ is the exposure time of the experiment. The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$. LISA~\citep{Audley:2017drz} and B-DEICIGO~\citep{10.1093/ptep/pty078} are proposed to be single detector interferometers, where as BBO~\citep{PhysRevD.72.083005} and DEICIGO~\citep{Sato_2017} would be built from an array of multiple interferometers.
GW signals produced from an early cosmological phase transition would be seen as a stocastic background. Assuming that the GW follows a power law background in frequency, it is commonplace to quote the power law integrated (PLI) sensistivity curves~\cite{PhysRevD.88.124032}. the PSI curves are constructed using information from the power law form of the signal,
h^2 \Omega_{\textrm{GW}}(f) = h^2 \Omega_{\beta}  \bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta}
where $\beta$ is the spectral index of the power law, and $f_{\textrm{ref}}$ is an arbitrary reference frequency which has no effect on the PLI sensetivities. 
The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn:RelaDOF}), for various spectral indices $\beta \in (-8,-7,-6, ... , 6, 7, 8)$ and for some fixed threshold value of $\rho_{th}$. Each curve will lay tangent to the PSI curve, more formally,
h^2 \Omega_{\textrm{PLI}} = \max\limits_{\beta}\bigg[ h^2 \Omega_{\beta}\bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta}  \bigg].

@@

\section{Conclusion}
\label{sec:conclusion}

@@

We can think of these results providing 
This demonstrates the power of GW signals to probe deep into the unknown arena of complex hidden sectors --- whether there are 1, 5, or more hidden sectors 

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\bibliographystyle{apsrev4-1}
\bibliography{refs}
